A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-11-06 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp-main.tex
Use more standard language for "near-real" time (referee comment)

At the same time, trigger systems for next-generation experiments are
evolving to be more capable, both in their ability to select a wider
range of events of interest for the physics programme, and their ability
to stream a larger rate of events for further processing. ATLAS and CMS
both target systems where the output of the hardware trigger system is
increased by an order of magnitude over the current capability, up to 1
MHz~\cite{CERN-LHCC-2015-020,CMSCollaboration:2015zni}. In LHCb~\cite{CERN-LHCC-2014-016}
and ALICE~\cite{Buncic:2011297}, the full collision
rate (between 30 to 40 MHz for typical LHC proton-proton operations)
will be streamed to real-time or quasi-real-time software trigger
systems. The increase in event complexity also brings a ``problem'' of
an overabundance of signals to the experiments, and specifically to the
software trigger algorithms. The evolution towards a genuine real-time
analysis of data has been driven by the need to analyse more signal than
can be written out for traditional processing, and technological
developments that enable this without reducing the analysis sensitivity
or introducing biases.

>>>>

At the same time, trigger systems for next-generation experiments are
evolving to be more capable, both in their ability to select a wider
range of events of interest for the physics programme, and their ability
to stream a larger rate of events for further processing. ATLAS and CMS
both target systems where the output of the hardware trigger system is
increased by an order of magnitude over the current capability, up to 1
MHz~\cite{CERN-LHCC-2015-020,CMSCollaboration:2015zni}. In LHCb~\cite{CERN-LHCC-2014-016}
and ALICE~\cite{Buncic:2011297}, the full collision
rate (between 30 to 40 MHz for typical LHC proton-proton operations)
will be streamed to real-time or near-real-time software trigger
systems. The increase in event complexity also brings a ``problem'' of
an overabundance of signals to the experiments, and specifically to the
software trigger algorithms. The evolution towards a genuine real-time
analysis of data has been driven by the need to analyse more signal than
can be written out for traditional processing, and technological
developments that enable this without reducing the analysis sensitivity
or introducing biases.
